\section{Band Planning}
    \subsection{General Information}
    The band and relevant staff consists of 10 musicians, 12 crew, 1 photographer, and 3 drivers. They've requested 6 hours from load in to the end of sound check for their setup time requirements. A PA with \SI{115}{\decibel\A} \gls{spl} full range with even coverage was requested. A separate control over the L/R matrix, front fills and subs will be provided. Another consideration is that the monitor engineer requested access to waves soundgrid plugins.

    \subsection{Staffing Requirements}
    The band specified that all staff should be experienced, professional and speak good English. Table \ref{tab:staffing} shows the staff required.

    \begin{longtable}[H]{|l|l|}
        \hline
        \textbf{Quantity} & \textbf{Staff} \\ \hline
        \endfirsthead
        %
        \endhead
        %
        8 & Stage hands for load in/out and changeover \\ \hline
        1 & Rigger \\ \hline
        2 & Lighting engineers \\ \hline
        2 & Audio engineers \\ \hline
        1 & Electrician \\ \hline
        1 & House spot \\ \hline
        1 & Runner with good knowledge of the area \\ \hline

        \caption{Staffing Requirements}
        \label{tab:staffing}
    \end{longtable}
    
    \subsection{Patch Sheet}
    Patch sheet located at Appendix (\ref{appendix:patch_sheet}). 

    \subsection{Area and Riser Requirements}
    For the main stage, the roof, sides and back wall will have black weather proof covers installed. On both the stage and wings, the area will be well lit with handrails. The band requested minimum requirements for each area however, larger areas are specified above in Table \ref{tab:amenities_calcs}.

    \begin{longtable}[H]{|l|l|l|l|}
        \hline
        \textbf{Area} & \textbf{Length} & \textbf{Width} & \textbf{Height} \\ \hline
        \endfirsthead
        %
        \endhead
        %
        Main Stage & \SI{12}{\metre} & \SI{10}{\metre} & \SI{1.5}{\metre} \\ \hline
        Wing \gls{sr} & \SI{4.5}{\metre} & \SI{3}{\metre} & - \\ \hline
        Wing \gls{sl} & \SI{5}{\metre} & \SI{3}{\metre} & - \\ \hline
        \gls{foh} (Audio) & \SI{5}{\metre} & \SI{3}{\metre} & - \\ \hline
        \gls{foh} (Lighting) & \SI{5}{\metre} & \SI{2}{\metre} & \SI{1}{\metre} \\ \hline
        \caption{Minimum Area Requirements}
        \label{tab:area_requirements}
    \end{longtable}

    \begin{longtable}[H]{|l|lll|}
        \hline
        \textbf{Quantity} & \multicolumn{1}{l|}{\textbf{Length}} & \multicolumn{1}{l|}{\textbf{Width}} & \textbf{Height} \\ \hline
        \endfirsthead
        %
        \endhead
        %
        2 & \multicolumn{1}{l|}{8ft} & \multicolumn{1}{l|}{8ft} & 1ft \\ \hline
        2 & \multicolumn{1}{l|}{8ft} & \multicolumn{1}{l|}{8ft} & 2ft \\ \hline
        1 & \multicolumn{1}{l|}{8ft} & \multicolumn{1}{l|}{12ft} & 2ft \\ \hline
        2 & \multicolumn{1}{l|}{8ft} & \multicolumn{1}{l|}{4ft} & 2ft \\ \hline
        2 & \multicolumn{3}{l|}{Small 2ft treads/steps} \\ \hline
        \caption{Riser Requirements}
        \label{tab:riser_requirements}
    \end{longtable}

    \subsection{Monitor Requirements}
    The band specified \gls{iem} with 10 stereo mixes over 2 bands minimum. No wedges will be required however, they do specify 2 sub sidefills. These are placed at the sides of the stage, facing the performers which creates a more natural on-stage experience and provides the physical sensation of bass frequencies.