\section{Introduction}
    This report demonstrates the planning of a hypothetical large-scale (50,000 - 100,000 people) outdoor music event, including the entire event setup and system design for a specified band. Utilizing ArrayCalc to design a speaker system for the event. Equipment will be carefully chosen based on the band's requirements and comparative research. Excel will be employed to create a comprehensive patch sheet, outline the system integration and calculate power requirements. Finally, a risk assessment will be formulated using Microsoft Word to identify necessary precautions.

    \subsection{Aims}
    The aim of this report is to plan and design various aspects of a large-scale outdoor music festival. This report will explain the rationale behind the selection of specific equipment and decisions over alternatives, aiming to craft a detailed design that ensures an optimal experience.
    
    \subsection{Objectives}
        \begin{itemize}
            \item Specify technical requirements for the event (such as microphones, desks, stage boxes, amplifiers and loudspeakers), tailoring the equipment for a specified band and venue.
            \item Design a bespoke speaker system for an outdoor venue and calculate the \gls{spl}, taking health and safety requirements into consideration.
            \item Justify equipment choices through meticulous research and evaluation of technical specifications, bearing in mind the band's equipment specifications.
            \item Identify and compare suitable audio networking solutions and protocols, while integrating redundancy within the system integration plan.
            \item Calculate power requirements, choose appropriate generators, and explore eco-friendly options.
        \end{itemize}